Case 4

### 2017-09-15 EU-Circle/eu-circle_case-study-4.Rmd
EU-Circle case study 4
mimoza + Bangladesh

Correlation between storm tracks and stations.

@@

>>>>

Look at correlation between storm tracks and stations. Also see if there is a connection between wind speed, cycvlone size, etc and the temperature (Indian Ocean, global mean). Possible to estimate a scaling function that can be applied to historical storms? Based on a large sample of data, such as the North Atlantic?

@@

We can use similar approach as in Benestad et al. (2017) <http://www.nat-hazards-earth-syst-sci.net/17/993/2017/> to downscale the local sea level. This, however, does not account for the global increase, which needs to be analysed seperately and added to this.
